A biometric analysis of infant mortality and temperature, northern Sweden 1895-1950

### 2022-01-03 paper.Rmd
continuations ...
enhance g-transform plot

We plot without the first step in the left hand panel and with it in the
right hand panel, see Figure \@ref(fig:ggplot2).

```{r ggplot2, fig.cap = "BB plots with and without time transform.", fig.height = 7}
nbths <- NROW(infdat)
oldpar <- par(mfrow = c(2, 1))
sur <- with(infdat, Surv(enter, exit, event))
rs <- risksets(sur)
ss <- cumsum(rs$n.events)
## Natural:
xt <- rs$risktimes
att <- c(0, 28, 183, 365)
plot(xt, ss / nbths, ylim = c(0, max(ss / nbths)), type = "l",
     axes = FALSE, col = "blue", lwd = 2, xlab = "Age (days)",
     main = "Untransformed", ylab = "Cum. deaths")
abline(h = 0)
axis(2, las = 1)
axis(1, at = att, labels = att)
box()
## g-transformed:
plot(g(xt), ss / nbths, ylim = c(0, max(ss / nbths)), type = "l",
     axes = FALSE, col = "blue", lwd = 2, xlab = "Age (days)",
     main = "After g-transform", ylab = "Cum. deaths")
abline(h = 0)
axis(2, las = 1)
axis(1, at = g(att), labels = att)
box()
##
par(oldpar)
```

>>>>

We plot without the first step in the top panel and with it in the
bottom panel, see Figure \@ref(fig:ggplot2).

```{r ggplot2, fig.cap = "BB plots with and without time transform.", fig.height = 5}
nbths <- NROW(infdat)
##oldpar <- par(mfrow = c(2, 1))
sur <- with(infdat, Surv(enter, exit, event))
rs <- risksets(sur)
ss <- cumsum(rs$n.events)
## Natural:
xt <- rs$risktimes
att <- c(0, 28, 183, 365)
plot(xt, ss / nbths, ylim = c(0, max(ss / nbths)), type = "l",
     axes = FALSE, col = "blue", lwd = 2, xlab = "Age (days)",
     ylab = "Cum. deaths")
abline(h = 0)
axis(2, las = 1)
axis(1, at = att, labels = att)
box()
## g-transformed:
lines(g(xt) / g(365) * 365, ss / nbths, ylim = c(0, max(ss / nbths)), type = "l",
     col = "red", lwd = 2, xlab = "Age (days)",
     main = "After g-transform", ylab = "Cum. deaths")
##abline(h = 0)
##axis(2, las = 1)
axis(3, at = g(att) / g(365) * 365, labels = att, col = "red")
box()
abline(v = 0)
abline(v = g(c(28, 183, 365)) / g(365) * 365, col = "red", lty = 3)
abline(v = c(28, 183, 365), col = "blue", lty = 3)
##
legend("bottomright", legend = c("Natural", "g-transform"), col = c("blue", "red"), lty = 1)
abline(h = (ss / nbths) [28], lty = 3 )
abline(h = (ss / nbths) [180], lty = 3 )
##par(oldpar)
```
